Supplementary Material

### 2020-01-30 Appendix_S4.Rmd
omitted personal identifying information for double-blind peer review at Am Nat

---
output:
  pdf_document:
    keep_tex: false
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
header-includes:
  - \usepackage{fullpage}
  - \linespread{1.5} 
  - \usepackage{lineno}
  - \usepackage{caption,setspace} # sets spread to 1 within captions
  - \captionsetup[figure]{font=small,labelformat=empty}
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$ \normalsize \end{center}

@@

>>>>

---
output:
  pdf_document:
    keep_tex: false
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
header-includes:
  - \usepackage{fullpage}
  - \linespread{1.7} 
  - \usepackage{lineno}
  - \usepackage{caption,setspace} # sets spread to 1 within captions
  - \captionsetup[figure]{font=small,labelformat=empty}
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

<!-- remove for double-blind peer review
\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$ \normalsize \end{center}

@@

\bigskip
-->
